---
title: "Surveillance Watch"
subtitle: "Public records on U.S. surveillance authorities, checked weekly. Primary sources first."
execute:
  echo: false
  warning: false
  message: false
---

```{r setup}
library(dplyr)
library(readr)
library(stringr)
library(knitr)

seen <- if (file.exists("data/seen.csv")) {
  read_csv("data/seen.csv", col_types = "cccccc")
} else {
  tibble(source_id = character(), item_id = character(), title = character(),
         url = character(), date = character(), first_seen = character())
}

status <- if (file.exists("data/run_status.csv")) {
  read_csv("data/run_status.csv", col_types = "ciici")
} else NULL

failures <- if (file.exists("data/failures.csv")) {
  read_csv("data/failures.csv", col_types = "ccc")
} else NULL

source("R/sources.R")
source_names <- setNames(
  vapply(SOURCES, function(s) s$name, character(1)),
  vapply(SOURCES, function(s) s$id, character(1))
)

linked <- seen |>
  mutate(
    source = source_names[source_id],
    item = paste0("[", str_trunc(title, 110), "](", url, ")")
  ) |>
  arrange(desc(first_seen))
```

```{r status-line, results='asis'}
if (!is.null(status)) {
  cat(sprintf(
    "**Last check:** %s &nbsp;·&nbsp; **%d** of **%d** sources reachable &nbsp;·&nbsp; **%d** new item(s)\n",
    status$last_run, status$sources_ok, status$sources_all, status$new_items
  ))
} else {
  cat("**No runs recorded yet.** Trigger the `check-sources` workflow (Actions tab → Run workflow) or run `Rscript R/run_check.R` locally.\n")
}
```

## New this week

```{r new-items, results='asis'}
cutoff <- as.character(Sys.Date() - 8)
fresh <- filter(linked, first_seen >= cutoff)
if (nrow(fresh) == 0) {
  cat("_Nothing new since the last check._\n")
} else {
  fresh |>
    select(`First seen` = first_seen, Source = source, Item = item) |>
    kable()
}
```

## Full record by source

```{r by-source, results='asis'}
if (nrow(linked) == 0) {
  cat("_No items recorded yet._\n")
} else {
  for (sid in unique(linked$source_id)) {
    block <- filter(linked, source_id == sid)
    cat("\n###", source_names[[sid]], "\n\n")
    print(kable(select(block, `First seen` = first_seen, Item = item) |> head(15)))
    cat("\n")
  }
}
```

## Source health

```{r failures, results='asis'}
if (is.null(failures) || nrow(failures) == 0) {
  cat("_No source failures logged._\n")
} else {
  failures |>
    arrange(desc(date)) |>
    head(20) |>
    select(Date = date, Source = source_id, Error = error) |>
    kable()
}
```

---

*What this site is: an automated weekly check of primary public records: the [Federal Register](https://www.federalregister.gov) (new executive orders and documents citing EO 12333), the [FISA Court public docket](https://www.fisc.uscourts.gov/public-filings) (declassified opinions, including compliance findings), [ODNI press releases](https://www.dni.gov/index.php/newsroom/press-releases) (annual transparency reports), [PCLOB](https://www.pclob.gov) oversight reports, [Congress.gov](https://www.congress.gov) (FISA-related bills), plus analysis feeds from Lawfare and EFF. Raw copies of everything fetched are archived in the repository, because public documents sometimes disappear.*
